---
title: "Rpackage"
author: "Andrew Liu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rpackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
Install \texttt{Rpackage} using:
```{r, eval = FALSE}
devtools::install_github("Zhaoyu-Andrew/Rpackage")
```
To begin, we load our example data set as a \texttt{gapminder} object.

```{r, message = FALSE}
library(Rpackage)
```
If you are unfamiliar with \texttt{my_gapminder}, we can view a description of the data using:

```{r}
head(my_gapminder)
```
# Fitting a t-test
Now, let's set up our model. 
First, let's subset our samples to only include lifeExp covariate
```{r}
life_Exp <- my_gapminder[[4]]
my_t.test(life_Exp, "two.sided", 60)

my_t.test(life_Exp, "less", 60)

my_t.test(life_Exp, "greater", 60)
```
# Interpreting the result of the t-test

Test 1: 
  for the two-sided test, since the p-value 0.09322877 is greater than the cut-off value of α =0.05,
  we conclude that we fail to reject the null hypothesis, therefore, there is not sufficient evidence to
  support a conclusion that the population mean differs from a life expectancy of 60 years. 
  
Test 2:
  for the left-sided test, since the p-value 0.04661438 is less than the cut-off value of α =0.05,
  we reject the null hypothesis, therefore, there is enough evidence to support a conclusion that the 
  population mean is less than a life expectancy of 60 years. 
  
Test 3:
  for the right-sided test, since the p-value 0.9533856 is greater than the cut-off value of α =0.05,
  we conclude that we fail to reject the null hypothesis, therefore, there is not sufficient evidence to
  support a conclusion that the population mean is greater than a life expectancy of 60 years. 
```{r}
library(ggplot2)
library(tidyverse)
gdp_Percap <- my_gapminder[[6]]
continent <- my_gapminder[[2]]
my_lm <- my_lm(life_Exp ~ gdp_Percap + continent, data = my_gapminder)



my_lm_data_frame <- as.data.frame.matrix(my_lm) 
mod_fits <- fitted(my_lm_data_frame)
my_df <- data.frame(actual = my_gapminder$lifeExp, fitted = mod_fits)
ggplot(my_df, aes(x = fitted, y = actual)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0, col = "red", lty = 2) + 
  theme_bw(base_size = 15) +
  labs(x = "Fitted values", y = "Actual values", title = "Actual vs. Fitted") +
  theme(plot.title = element_text(hjust = 0.5))

```
